Douglas-complex fire smoke and cardiopulmonary morbidity

### 2017-11-15 r_scripts/analysis/oregon_cvd_pulm_results.Rmd
stuff

```{r descriptive table}
# creating a row calculation function
table1_fun <- function(data_list){
  # output of total n
  total_n <- data_list %>% 
    filter(outcome == 1) %>%
    summarise(total_n = n())

@@

```{r distributed lag function}
# custom distributed lag function 
distributed_lag <- function(data, pm_df, temp_df, cumulative=T){
  # limit to complete cases
  complete_data <- data %>% 
    # filter to complete case for smoke
    filter(!is.na(geo_smk_pm_lag7_zip))

@@

@@

##9. Conculstions
So far, it looks like SABA and Asthma are the only associtions. Furthermore, the cumulative 0-7 day relationship between asthma and smoke has wide error bars and overlaps 1, suggesting the association could be null. I think it's more likely that this is because we introduce some noise on lag days 4-7. It's possible that an adjustment like weekend may help. It may also make sense to do something similar to Anna Rappold or others and shorten our lagged response. I also think this is a produce of sample size too.

>>>>

```{r descriptive table}
# creating a row calculation function
table1_fun <- function(data_list){
  data_list <- data_list %>%
    filter(!is.na(geo_smk_pm_zip))

  # output of total n
  total_n <- data_list %>%
    filter(outcome == 1) %>%
    summarise(total_n = n())

@@

```{r distributed lag function}
# custom distributed lag function 
distributed_lag <- function(data, pm_df, temp_df, cumulative=T){

  # limit to complete cases
  complete_data <- data %>%
    # filter to complete case for smoke
    filter(!is.na(geo_smk_pm_lag7_zip))

@@

```{r same day stratified sex function}
same_day_sex_fun <- function(data_list){
  data_list <- data_list %>%
    filter(!is.na(geo_smk_pm_zip)) %>%
    mutate(geo_smk10 = geo_smk_pm_zip/10)

  # Male
  data_M <- data_list %>%
    filter(sex_ind == 0)

  # fit model with basis ----
  mod_M <- clogit(outcome ~ geo_smk10 + wrf_temp_zip + strata(personkey),
                  data = data_M)

  # odds ratio
  estimates_M <- round(exp(summary(mod_M)$coefficient[1,1]), 3) # sd stands for same day

  # 95% lower bound
  lower95_M <- round(exp((summary(mod_M)$coefficient[1,1]) -
                                    1.96*(summary(mod_M)$coefficient[1,3])), 3)
  # 95% upper bound
  upper95_M <- round(exp((summary(mod_M)$coefficient[1,1]) +
                                    1.96*(summary(mod_M)$coefficient[1,3])), 3)
  # standard error
  sd_stderr_M <- round(summary(mod_M)$coefficient[1,3], 4)
  # p val
  sd_pvalue_M <- round(summary(mod_M)$coefficient[1,5], 4)

  total_n_M <- data_M %>%
    filter(outcome == 1) %>%
    summarise(total_n = n())

  # Female
  data_F <- data_list %>%
    filter(sex_ind == 1)

  # fit model with basis ----
  mod_F <- clogit(outcome ~ geo_smk10 + wrf_temp_zip + strata(personkey),
                  data = data_F)

  # odds ratio
  estimates_F <- round(exp(summary(mod_F)$coefficient[1,1]), 3) # sd stands for same day

  # 95% lower bound
  lower95_F <- round(exp((summary(mod_F)$coefficient[1,1]) -
                                    1.96*(summary(mod_F)$coefficient[1,3])), 3)
  # 95% upper bound
  upper95_F <- round(exp((summary(mod_F)$coefficient[1,1]) +
                                    1.96*(summary(mod_F)$coefficient[1,3])), 3)
  # standard error
  sd_stderr_F <- round(summary(mod_F)$coefficient[1,3], 4)
  # p val
  sd_pvalue_F <- round(summary(mod_F)$coefficient[1,5], 4)

  total_n_F <- data_F %>%
    filter(outcome == 1) %>%
    summarise(total_n = n())

  ### try ---
  gender <- rbind(c("Male"), c("Female"))
  total_n <- rbind(total_n_M, total_n_F)
  estimate <- rbind(estimates_M, estimates_F)
  lower95 <- rbind(lower95_M, lower95_F)
  upper95 <- rbind(upper95_M, upper95_F)

  return_estimate <- tibble(total_n_F, estimates_F, lower95_F, upper95_F)

  return(return_estimate)
}

same_day_sex <- outcome_df_list %>%
  purrr::map(~same_day_sex_fun(.)) %>%
  plyr::rbind.fill() # %>%
#   bind_cols(., data_frame(rep(outcome_names, each=2))) %>%
#   rename(outcome_names = `rep(outcome_names, each = 2)`) %>%
#   select(outcome_names, return_estimate) %>%
  # preserve order of names
#   mutate(outcome_names = parse_factor(outcome_names, levels = outcome_names))

```

```{r r same day stratified sex plot}
dl_results <- outcome_df_list %>%
  purrr::map(~distributed_lag(.)) %>%
  plyr::rbind.fill() %>%
  bind_cols(., data_frame(rep(outcome_names, each=2))) %>%
  rename(outcome_names = `rep(outcome_names, each = 2)`) %>%
  select(outcome_names, gender, total_n, estimate, lower95, upper95) %>%
  # preserve order of names
  mutate(outcome_names = parse_factor(outcome_names, levels = outcome_names))

```

```{r same day stratified age function}

```

@@

```{r saba same day assciation function}

```

##9. Conculsions
So far, it looks like SABA and Asthma are the only associtions. Furthermore, the cumulative 0-7 day relationship between asthma and smoke has wide error bars and overlaps 1, suggesting the association could be null. I think it's more likely that this is because we introduce some noise on lag days 4-7. It's possible that an adjustment like weekend may help. It may also make sense to do something similar to Anna Rappold or others and shorten our lagged response. I also think this is a produce of sample size too.
